Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
corrections

	Constraints in Gecode are always evaluated ahead of a further growth of a subtree, as it may be possible to prune some of the subtrees. The problem here is to decide in which order the constraints should be considered, and it may even be necessary to evaluate some constraints more often. A short example will explain this very well \cite[p.~575]{handbookCP}: Let there be two constraints 
	\begin{equation}
		c_1: y - x^2 = 0
	\end{equation}
	\begin{equation}
		c_2: y - x - 1 = 0
	\end{equation}
	and let the variable domains be $x, y \in [-4, 4]$. Starting with the evaluation of constraint one follows a chain of reductions of the variable domains, based only on constraint propagation:
	\begin{equation}
	\begin{split}
		c_1:\ &y \in [-4, 4] \rightarrow y \in [0, 4] \\
		c_1:\ &x \in [-4, 4] \rightarrow x \in [-2, 2] \\
		c_2:\ &y \in [0, 4] \rightarrow y \in [0, 3] \\
		c_2:\ &x \in [-2, 2] \rightarrow x \in [-1, 2] \\
		c_1:\ &x \in [-1, 2] \rightarrow x \in [-1, 1.73 \dots] \\
		&\dots
	\end{split}
	\end{equation}
	Actually this behaviour is very nice to have as it narrows the down the search space efficiently.

@@

	The next difficult decision is which constraint should evaluated first. In the example above the constraints were quite simple and therefore it won't make a difference to evaluate first $c_1$ or $c_2$, the search will take nearly the same time. Unfortunately not all constraints are that easy to evaluate and for this case Gecode sets for every constraint a certain cost \cite[p.~275]{programmingGecode}. Based on this cost the constraints are sorted into buckets which are then iterated from the constraints with lower costs to the ones with higher costs. This means, whenever a variable domain is changed, the first try is to use constraints with the lowest possible cost and only if none of them needs to be evaluated constraints with higher costs are considered.

>>>>

	Constraints in Gecode are always evaluated ahead of a further growth of a subtree, as it may be possible to prune some of the subtrees. The problem here is to decide in which order the constraints should be considered, and it may even be necessary to evaluate some constraints more often. A short example will explain this very well \cite[p.~575]{handbookCP}: Let there be two constraints 
	\begin{equation}
		c_1: y - x^2 = 0
	\end{equation}
	\begin{equation}
		c_2: y - x - 1 = 0
	\end{equation}
	and let the variable domains be $x, y \in [-4, 4]$. Starting with the evaluation of constraint one follows a chain of reductions of the variable domains, based only on constraint propagation:
	\begin{equation}
	\begin{split}
		c_1:\ &y \in [-4, 4] \rightarrow y \in [0, 4] \\
		c_1:\ &x \in [-4, 4] \rightarrow x \in [-2, 2] \\
		c_2:\ &y \in [0, 4] \rightarrow y \in [0, 3] \\
		c_2:\ &x \in [-2, 2] \rightarrow x \in [-1, 2] \\
		c_1:\ &x \in [-1, 2] \rightarrow x \in [-1, 1.73 \dots] \\
		&\dots
	\end{split}
	\end{equation}
	Actually this behaviour is very nice to have as it narrows efficiently the search space down.

@@

	The next difficult decision is which constraint should be evaluated first. In the example above the constraints were quite simple and therefore it won't make a big difference to evaluate first $c_1$ or $c_2$, the search will take nearly the same time. Unfortunately not all constraints are that easy to evaluate and for this case Gecode defines for every constraint a certain cost \cite[p.~275]{programmingGecode}. Based on this cost the constraints are sorted into buckets which are then iterated from the constraints with lower costs to the ones with higher costs. This means, whenever a variable domain is changed, the first try is to use constraints with the lowest possible cost and only if none of them needs to be evaluated constraints with higher costs are considered.
